### 2014-03-01 paper/concrete.tex
notation fixes.

  \begin{mathpar}
    \inferrule[C-fork]
    {
      \text{|ie| does not contain any |ta|}\\
      |iS' = iS [ id' mapsto nil ]|\\
      |it1 = oneheapfullconf id il (iniE id')|\\
      |itnew = oneheapfullconf id' il (TI ie)|\\
      |fresh (id')|
    }
    {|
      oneheapiconf iS tS (oneheapfullconf id1 il1 (iniEi (fork ie)), ldots)
      .->
      iS'; tS; sched F (it1, ldots, itnew)
    |}
    \and
    \inferrule[C-send]
    {
      \text{|ie| does not contain any |ta|}\\
      |il canFlowTo il'|\\
      |iS(id') = Q|\\
      |iS' = iS [ id' mapsto (il', id,  ie) , Q ]|
    }
    {|
      oneheapiconf iS tS (oneheapfullconf id il (iniEi (send id' il' ie)), ldots)
      ->
      iS; tS; sched step (oneheapfullconf id il unit, ldots)
    |}
  \end{mathpar}

>>>>

  \begin{mathpar}
    \inferrule[C-fork]
    {
      \text{|ie| does not contain any |ta|}\\
      |iS' = iS [ mapsto id' nil ]|\\
      |it1 = oneheapfullconf id il (iniE id')|\\
      |itnew = oneheapfullconf id' il (TI ie)|\\
      |fresh (id')|
    }
    {|
      oneheapiconf iS tS (oneheapfullconf id1 il1 (iniEi (fork ie)), ldots)
      .->
      iS'; tS; sched F (it1, ldots, itnew)
    |}
    \and
    \inferrule[C-send]
    {
      \text{|ie| does not contain any |ta|}\\
      |il canFlowTo il'|\\
      |iS(id') = Q|\\
      |iS' = iS [ mapsto id' (il', id,  ie) , Q ]|
    }
    {|
      oneheapiconf iS tS (oneheapfullconf id il (iniEi (send id' il' ie)), ldots)
      ->
      iS; tS; sched step (oneheapfullconf id il unit, ldots)
    |}
  \end{mathpar}

### 2014-03-01 paper/formal.tex
notation fixes.

\begin{figure} % fig:erasure
\begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))|\\
  &|fullconf id il' tS ie| \begin{cases}
    |bullet| & |il' cantFlowTo il| \\
    |fullconf id il' tS ie| & \text{otherwise}
  \end{cases} \\
  &|erase il emptyset = emptyset|\\
  &|erase il (iS [id mapsto Q]) =| \begin{cases}
    |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
    & \text{the label of thread |id|} \\
    |(erase il iS) [id mapsto (erase il Q)]| & \text{otherwise}
  \end{cases} \\
  &|erase il Q = filter il Q|\\
  &|erase il v = v|
\end{align*}
\caption{ Erasure function for tasks, queue maps, message queues, and
configurations.  In all other cases, including target-language constructs,
|erasef il| is applied homomorphically.  \label{fig:erasure} }
\end{figure}

>>>>

\begin{figure} % fig:erasure
\begin{align*}
  &|erase il (iconf iS its) =
  iconf (erase il iS) (fltr (\ it . it = bullet) (map (erasef il) its))|\\
  &|fullconf id il' tS ie| \begin{cases}
    |bullet| & |il' cantFlowTo il| \\
    |fullconf id il' tS ie| & \text{otherwise}
  \end{cases} \\
  &|erase il emptyset = emptyset|\\
  &|erase il (iS [mapsto id Q]) =| \begin{cases}
    |erase il iS| & \text{|il' cantFlowTo il|, where |il'| is}\\
    & \text{the label of thread |id|} \\
    |(erase il iS) [mapsto id (erase il Q)]| & \text{otherwise}
  \end{cases} \\
  &|erase il Q = filter il Q|\\
  &|erase il v = v|
\end{align*}
\caption{ Erasure function for tasks, queue maps, message queues, and
configurations.  In all other cases, including target-language constructs,
|erasef il| is applied homomorphically.  \label{fig:erasure} }
\end{figure}

### 2014-03-01 paper/retrofit.tex
notation fixes.

\and
\inferrule[T-ref]
{ }
{| conf tS (ref tv) -> conf (tS [ ta mapsto tv ]) ta |}
{| fresh ta |}

@@

\and
\inferrule[T-ass]
{ |(ta, tv) in tS| }
{| conf tS (ta := tv) -> conf (tS [ ta mapsto tv ]) tv |}

@@

\begin{figure}
\begin{code}
lop  ::=  canFlowTo | lub | glb
iv   ::=  id | il | true | false | unit
ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie
       |  sandbox ie | send ie ie ie | ix1, ix2 <= recv. ie ie
iE   ::=  iHole | iE lop ie | iv lop iE | setLabel iE | sandbox iE 
       |  send iE ie ie | send iv iE ie | send iv iv iE
       |  ix1, ix2 <= recv. ie ie
io   ::=  (il, id ie)
Q    ::=  nil | io , Q
iS   ::=  emptyset | iS [ id mapsto Q ]
\end{code}

@@

\and
\inferrule[I-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ id' mapsto (il', id,  ie) , Q ]|
}
{|
niconf iS  id il (send id' il' ie)
->
niconf iS' id il unit
|}

\and
\inferrule[I-recv]
{
| filter il (iS(id)) = io1 , ... , iok , (il', id', ie')|\\
| iS' = iS[id mapsto io1 , ... , iok]|\\
}
{|
niconf iS  id il (ix1, ix2 <= recv. ie1 ie2)
->
niconf iS' id il ({ie'/ix1,id'/ix2} ie1)
|}

\and
\inferrule[I-noRecv]
{
| filter il (iS(id)) = nil|\\
| iS' = iS[id mapsto nil]|
}
{|
niconf iS  id il (ix1, ix2 <= recv. ie1 ie2)
->
niconf iS' id il ie2
|}

@@

\begin{mathpar}
\inferrule[I-sandbox]
{ 
|iS' = iS [ id' mapsto nil ]|\\
|tS' = klone(tS)|\\
|it1 = fullconf id il tS (iniE id')|\\
|itnew = fullconf id' il tS' (TI ie)|\\
|fresh (id')|
}
{|
iconf iS (fullconf id il tS (iniEi (sandbox ie)), ldots)
.->
iS'; sched F (it1, ldots, itnew)
|}

>>>>

\and
\inferrule[T-ref]
{ }
{| conf tS (ref tv) -> conf (tS [ mapsto ta tv ]) ta |}
{| fresh ta |}

@@

\and
\inferrule[T-ass]
{ |(ta, tv) in tS| }
{| conf tS (ta := tv) -> conf (tS [ mapsto ta tv ]) tv |}

@@

\begin{figure}
\begin{code}
lop  ::=  canFlowTo | lub | glb
iv   ::=  id | il | true | false | unit
ie   ::=  iv | ix | ie lop ie | getLabel | setLabel ie
       |  sandbox ie | send ie ie ie | ix1, ix2 <= recv. ie ie
iE   ::=  iHole | iE lop ie | iv lop iE | setLabel iE | sandbox iE 
       |  send iE ie ie | send iv iE ie | send iv iv iE
       |  ix1, ix2 <= recv. ie ie
io   ::=  (il, id ie)
Q    ::=  nil | io , Q
iS   ::=  emptyset | iS [ mapsto id Q ]
\end{code}

@@

\and
\inferrule[I-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ mapsto id' (il', id,  ie) , Q ]|
}
{|
niconf iS  id il (send id' il' ie)
->
niconf iS' id il unit
|}

\and
\inferrule[I-recv]
{
| filter il (iS(id)) = io1 , ... , iok , (il', id', ie')|\\
| iS' = iS[mapsto id (io1 , ... , iok)]|\\
}
{|
niconf iS  id il (ix1, ix2 <= recv. ie1 ie2)
->
niconf iS' id il ({ie'/ix1,id'/ix2} ie1)
|}

\and
\inferrule[I-noRecv]
{
| filter il (iS(id)) = nil|\\
| iS' = iS[mapsto id nil]|
}
{|
niconf iS  id il (ix1, ix2 <= recv. ie1 ie2)
->
niconf iS' id il ie2
|}

@@

\begin{mathpar}
\inferrule[I-sandbox]
{ 
|iS' = iS [ mapsto id' nil ]|\\
|tS' = klone(tS)|\\
|it1 = fullconf id il tS (iniE id')|\\
|itnew = fullconf id' il tS' (TI ie)|\\
|fresh (id')|
}
{|
iconf iS (fullconf id il tS (iniEi (sandbox ie)), ldots)
.->
iS'; sched F (it1, ldots, itnew)
|}
